Descriptive_Stats

### 2023-09-15 Code/RankComparison.Rmd
Added womens clusrank results to bottom

>>>>

```{r}
women_data <- read.csv("../Data/WomenClusrank2019vs2022.csv")
colnames(women_data) <- c("Time", "Athlete", "Year")
```

```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = women_data,
                method = "ds")
clusWilcox.test(Time, group=Year, cluster = Athlete, data = women_data,
                method = "ds", 
                exact = TRUE, B = 10000)
```
